---
title: "Integral Projection Model"
author: "Loïc Pages & Eric Imbert"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---
Import models for vital rates (see ModelSelectionReport.Rmd)

Estimations per population and per year => IPM_Kernal_Pop_Year.RData
Estimation per year pooling data over populations => IPM_Kernal_Year.RData
Estimation per populations => IPM_Kernal_Pop.RData

```{r setup, include=FALSE}
rm(list=ls())
library(splines)
library(tidyverse)
library(spaMM)
library(popbio)

MatrixDim <- 50
AgeMax <- 8
spaMM.options(separation_max=70)

#Load the selected models
load("VitalRates.RData")
```

Creation of the functions for the kernels. 
```{r}
annees <- 1995:2021
populations <- c("Po","Au","Pe","E1","E2","Cr")

#Fecundity
numbofcap <- function(x, a, year) {
  fake_data <- expand.grid(
  year = year,
  Size0Mars = unique(x),
  Age = a)
  predi <- exp(predict(Fecundity, fake_data))
  meanpredi <- aggregate(predi, list(fake_data$Size0Mars), mean)
  nbcap <- ifelse(meanpredi$V1>=0,meanpredi$V1,0)
  return(matrix(nbcap, length(x), length(x), byrow = T))
}


#Survival Probability for age 1
sx01 <- function(x,a,Pop,year) {
  fake_data <- expand.grid(
  year = year,
  Pop = Pop,
  Size0Mars = unique(x),
  Age = a)
  predi <- predict(Seedling_surv, fake_data, allow.new.levels = T)
  meanpredi <- aggregate(predi, list(fake_data$Size0Mars), mean)
  return(meanpredi$V1)
}

#Survival Probability for age > 1
sx02 <- function(x,a,Pop,year) {
  fake_data <- expand.grid(
  year = year,
  Pop = Pop,
  Size0Mars = unique(x),
  Age = a)
  predi <- predict(Plant_surv, fake_data, allow.new.levels = T)
  meanpredi <- aggregate(predi, list(fake_data$Size0Mars), mean)
  return(meanpredi$V1)
}


#Flowering Probability
#Flowering function for The survival-growth kernel
flr0 <- function(x, a, Beta,Pop,year) {
  fake_data <- expand.grid(
  year = year,
  Pop = Pop,
  Size0Mars = unique(x),
  Age = a)
  predi <- plogis(predict(Flowering, newdata = fake_data, allow.new.levels = T, type = "link") + Beta)
  meanpredi <- aggregate(predi, list(fake_data$Size0Mars), mean)
  return(meanpredi$V1)
}

#Flowering function for fecundity fyx0 - same function the difference is in the format of the output
flr1 <- function(x, a, Beta,Pop,year) {
  fake_data <- expand.grid(
  year = year,
  Pop = Pop,
  Size0Mars = unique(x),
  Age = a)
  predi <- plogis(predict(Flowering, fake_data, allow.new.levels = T, type = "link") + Beta)
  meanpredi <- aggregate(predi, list(fake_data$Size0Mars), mean)
  return(matrix(meanpredi$V1, MatrixDim, MatrixDim, byrow = T))
}


#Growth (cumulative ditribution function)

Gyx <- function(ysup,yinf,x,a,Pop,year){  
  sizepow <- 0.4343354
  yinfpow <- yinf**sizepow
  ysuppow <- ysup**sizepow
  yinfpow[1] <- -Inf
  ysuppow[length(ysuppow)] <- Inf
  fake_data <- expand.grid(
  year = year,
  Pop = Pop,
  Size0Mars = unique(x),
  Age = a)
  predi <- predict(Growth, fake_data, allow.new.levels = T)
  meanpredi <- aggregate(predi, list(fake_data$Size0Mars), mean)
  
  resvar <- predict(Growth$resid_fit, newdata = fake_data, allow.new.levels = T)
  meanresvar <- aggregate(resvar[,1], list(fake_data$Size0Mars), mean)$x

  cdf.sup <- mapply(pnorm, mean = meanpredi$V1, sd = sqrt(meanresvar), MoreArgs = list(q=ysuppow))
  cdf.inf <- mapply(pnorm, mean = meanpredi$V1, sd = sqrt(meanresvar), MoreArgs = list(q=yinfpow))
  return(cdf.sup - cdf.inf)
}


densSeedl <- function(ysup, yinf,Pop,year) {
  yinf[1] <- -Inf
  ysup[length(ysup)] <- Inf
  fake_data <- expand.grid(
  year = year,
  Pop = Pop)
  
  mu <- predict(Seedling_size, newdata = fake_data)[, 1]
  shape <- 1 / Seedling_size$phi
  mu <- mean(mu)
  scale <- mu * Seedling_size$phi
  cdf.sup <- pgamma(ysup, shape = shape, scale = scale)
  cdf.inf <- pgamma(yinf, shape = shape, scale = scale)
  return(cdf.sup - cdf.inf)
}

Estbli <- function(Pop, year){
  fake_data <- expand.grid(
  year = year,
  Pop = Pop,
  Capitule = 1:200)
  plt <- predict(Estbrate, newdata = fake_data)[,1]
  mu <- mean(plt/fake_data$Capitule)
  return(mu)
}

#Combine fecundity and flowering probability 
fyx0 <- function(x , a, Beta = 0, Pop,year) {
  # Flowering probability:
  p.flow <- flr1(x, a, Beta,Pop,year)
  # Number of capitula per flowering plant
  n.captl <- numbofcap(x, a, year)
  # Establishment rate
  Estbl <- Estbli(Pop, year)

  feco <- p.flow * n.captl * Estbl
  return(feco)
}
```

```{r}
n.size <- MatrixDim
# Beta <- 0
# Pop <- "Au"
# year <- 2000
# age <- 5

K.fnc0 <- function(age, n.size, Beta=0, Pop,year){
  
  minsize <-  0.5
  maxsize <-  25
  maxsize1 <- 15
  h <-  (maxsize - minsize) / n.size
  h1 <-  (maxsize1 - minsize) / n.size
  b = minsize + c(0:n.size) * h

  #sizes for an individual of age a
  #midpoint
  ymid.a = 0.5 * (b[1:n.size] + b[2:(n.size + 1)])
  #intervals
  yI.a <- matrix(nrow = n.size, ncol = 2)
  for (i in 1:n.size){
    yI.a[i,1] <- b[i]
    yI.a[i,2] <- b[i+1]
  }
  
  b1 = minsize + c(0:n.size) * h1
  #sizes for an individual of age 1
  #midpoint
  ymid.1 = 0.5 * (b1[1:n.size] + b1[2:(n.size + 1)])
  #intervals
  yI.1 <- matrix(nrow = n.size, ncol = 2)
  for (i in 1:n.size){
    yI.1[i,1] <- b1[i]
    yI.1[i,2] <- b1[i+1]
  }
  
  if(age==1){ymid.a <- ymid.1
  # yI.a <- yI.1 
  h <- h1}
  
  #The growth kernel
  G <- Gyx(ysup=yI.a[,2], yinf=yI.a[,1], x=ymid.a, a=age, Pop=Pop, year=year)

  #The survival-growth kernel #remove flowering plants since they died
  sx0 <- ifelse(age==1,sx01,sx02)
  S_flr <- sx0(ymid.a,age, Pop=Pop, year=year)*(1-flr0(ymid.a,age,Beta, Pop=Pop, year=year))
  Ps <- sweep(G, MARGIN=2, S_flr, '*')
  P <- matrix(Ps, nrow=n.size)
  
  #Fecundity
  
  ProporSeedlSize <- densSeedl(ysup=yI.1[,2],yinf=yI.1[,1], Pop=Pop, year=year)
  feco <- fyx0(x = ymid.a, a = age, Beta = Beta, Pop=Pop, year=year)

  Fec <- sweep(feco, MARGIN=1, ProporSeedlSize, '*')

  IPMk <- P + Fec
  return(list(M=IPMk,Pk=P,Fk=Fec))
}
```

  
  the super matrix and growth rate
```{r}
super_matrix = function(Beta_test,Pop,year){
  Pk <- matrix(data = NA, nrow = MatrixDim, ncol = MatrixDim)
  Fk <- matrix(data = NA, nrow = MatrixDim, ncol = MatrixDim)
  Mk <- matrix(data = NA, nrow = MatrixDim, ncol = MatrixDim)
  Kernals <- array(data = 0, dim = c(AgeMax, 3, MatrixDim, MatrixDim))
  GlobMatrIPM <- array(0, dim = c((AgeMax * MatrixDim), (AgeMax * MatrixDim)))
  
  for (a in (1:(AgeMax - 1))){
    Kls <- K.fnc0(a, MatrixDim, Beta_test, Pop, year)
    Kernals[a, 1, , ] <- Kls$M
    Kernals[a, 2, , ] <- Kls$Pk
    Kernals[a, 3, , ] <- Kls$Fk
    # print(lambda(Kernals[a, 1, , ]))
    debut <- (a - 1) * MatrixDim + 1
    fin <- debut + (MatrixDim - 1)
    GlobMatrIPM[1:MatrixDim, (debut:fin)] <- Kls$Fk
    GlobMatrIPM[((fin + 1):(fin + MatrixDim)), (debut:fin)] <- Kls$Pk
  }
  
  Kls <- K.fnc0(AgeMax, MatrixDim, Beta_test, Pop, year)
  Kernals[AgeMax, 1, , ] <- Kls$M
  Kernals[AgeMax, 2, , ] <- Kls$Pk
  Kernals[AgeMax, 3, , ] <- Kls$Fk
  # print(lambda(Kernals[a,1,,]))
  debut <- (AgeMax - 1) * MatrixDim + 1
  fin <- debut + (MatrixDim - 1)
  GlobMatrIPM[1:MatrixDim, (debut:fin)] <- Kls$Fk
  GlobMatrIPM[(debut:fin), (debut:fin)] <- Kls$Pk
  
  return(GlobMatrIPM)
}
```


For each pop and for each year
```{r, warning=FALSE}
IPMKernalPopYear <- list()
k <- 1
for(i in 1:6) {
  for (j in 1:length(annees)) {
    # print(Pop[i])
    # print(annees[j])
    IPMKernalPopYear[[k]] <- super_matrix(0, populations[i], annees[j])
    k <- k+1
  }
}

k <- 1
for(i in 1:6) {
  for(j in 1:length(annees)) {
    nom <- paste(populations[i], annees[j], sep = "_")
    names(IPMKernalPopYear)[[k]] <- nom
    k <- k + 1
  }
}
```


```{r}
save(IPMKernalPopYear,file="IPM_Kernal_Pop_Year.RData")
```

Per year pooling populations
```{r, warning=FALSE}
IPMKernal_Year <- list()

for (j in 1:length(annees)) {
  IPMKernal_Year[[j]] <- super_matrix(0, populations, annees[j])
}

for(j in 1:length(annees)) {
  nom <- paste(annees[j])
  names(IPMKernal_Year)[[j]] <- nom
}

```

```{r}
save(IPMKernal_Year,file="IPM_Kernal_Year.RData")
```

Per population

```{r, warning=FALSE}
IPMKernal_Pop <- list()

for (p in 1:length(populations)) {
  IPMKernal_Pop[[p]] <- super_matrix(0, populations[p], annees)
}

for(p in 1:length(populations)) {
  nom <- paste(populations[p])
  names(IPMKernal_Pop)[[p]] <- nom
}

```

```{r}
save(IPMKernal_Pop,file="IPM_Kernal_Pop.RData")
```

